Top-Down Graph-Based Neuron Reconstruction

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: added qualitative results

The simplest node generation strategy creates one node for every unique segment label in the input volume. However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors. This typically happens in regions with noisy image data such that pixel-based methods could not generate the correct segments. It is difficult to extract useful shape features from these segments because of their small, and often random, shape. We prune these nodes from the graph by removing all segments with fewer than a threshold of $t_{seg}$ voxels. We use $t_{seg} = 20,000$ voxels, which removed on average XX\% \hp{add} of the segments in our  datasets (Sec.~\ref{sec:dataset}).

@@

A typical approach to generating edges produces an edge between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{} and GALA~\cite{} \hp{add refs} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. We identify a smaller number of pairs of segments to consider as graph edges using the following algorithm.

>>>>

The simplest node generation strategy creates one node for every unique segment label in the input volume. However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors. This typically happens in regions with noisy image data such that pixel-based methods could not generate the correct segments. It is difficult to extract useful shape features from these segments because of their small, and often random, shape. We prune these nodes from the graph by removing all segments with fewer than a threshold of $t_{seg}$ voxels. We use $t_{seg} = 20,000$ voxels, which removed on average 56\% of the segments in our  datasets (Sec.~\ref{sec:dataset}). Despite the large number of segments, these regions only take up 1.6\% of the total volume on average.

@@

A typical approach to generating edges produces an edge between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels where one has label $l_1$ and the other has label $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. We identify a smaller number of pairs of segments to consider as graph edges using the following algorithm.

### 2017-11-14 papers/cvpr2018/3_evaluation.tex
paper: added qualitative results

\noindent\textbf{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy. \hp{add ref} The mushroom body in this species is the major site of associative learning~\cite{takemura2017connectome}. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

@@

We use the first cylinder of the Kasthuri dataset \hp{check} for training and validation. We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of candidates. We apply data augmentation to the generated examples to increase the size of the training datasets. We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes. This produces 16 times more training data.

>>>>

\noindent\textbf{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

@@

We use the left cylinder of the Kasthuri dataset for training and validation. We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of candidates. We apply data augmentation to the generated examples to increase the size of the training datasets. We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes. This produces 16 times more training data.

### 2017-11-14 papers/cvpr2018/4_results.tex
paper: added qualitative results

@@

@@

\begin{figure}[t!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
	\caption{Example merge candidates.}
	\label{fig:skeleton-results}
\end{figure}

@@

\begin{table}
	\centering
	\begin{tabular}{c c c c} \hline
	\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
	Kasthuri Training & 0.919 & 0.936 & 0.974 \\
	Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
	FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\ 
	FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{table:classification}
\end{table}

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset. 
Figure \ref{fig:network-results} shows the receiver operating characteristic (ROC) curve for all four datasets.

\begin{figure}
	\includegraphics[width=0.9\linewidth]{./figures/roc-microns-300-test.png}
	\caption{(NOT CORRECT) The receiver operating characteristic (ROC) curve for all four datasets.}
	\label{fig:network-results}
\end{figure}

TODO - ADD QUALITATIVE RESULTS

@@

TODO - QUANTIFY IMPROVEMENT BY MULTICUT - READERS CAN SKIP SECTION FOR NOW

Using a graph-based optimization strategy prevents XX segments from merging compared to the simple hierarchical agglomeration strategy with an optimal threshold cut off. Since correcting merge errors is significantly more difficult than correcting split errors, it is desirable to limit the number of false merges. The graph-based strategies significantly improve this error type.

\subsection{Variation of Information Improvements}

We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
The input segmentation to our network serves as a baseline. 
We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
Similarly, we run the greedy-additive heuristic with varying parameters that increase the probability needed for merging nodes. 
Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
The oracles sees the entire constructed graph from our algorithm and correctly partitions the graph based on the ground truth. 
Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets. 
Table \ref{table:variation-of-information} provides a quantitative overview for the changes in variation of information.

TODO - ADD QUALITATIVE RESULTS

\begin{table}
	\centering
	\begin{tabular}{c c c} \hline
		\textbf{Dataset} & \textbf{VI Split} & \textbf{VI Merge} \\ \hline
		Kasthuri Training &  & \\
		Kasthuri Testing & & \\
		FlyEM Vol. 1 & & \\
		FlyEM Vol. 2 & & \\ \hline
	\end{tabular}
	\caption{Variation of Information Change}
	\label{table:variation-of-information}
\end{table}

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-train.png}
	\hspace{0.085\linewidth}
	\includegraphics[width=0.42\linewidth]{./figures/variation_of_information-test.png}
	\caption{The improvement on variation of information from the baseline NeuroProof segmentation (green). Results closer to the origin are better.}
	\label{fig:variation-of-information}
\end{figure*}

>>>>

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-train-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-microns-test-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-train-600.png}
	\includegraphics[width=0.23\linewidth]{./figures/variation_of_information-FlyEM-test-600.png}
	\caption{Our improvement (reD) on variation of information from the baseline NeuroProof segmentation (green). The blue dot represents an oracle which correctly partitions the graph.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\subsection{Variation of Information Improvement}

We compute the variation of information for our segmentations against the expert-labeled ground truth datasets. 
The input segmentation to our network serves as a baseline. 
We evaluate NeuroProof (our input) at several different thresholds to create a variation of information curve. 
Figure \ref{fig:variation-of-information} shows the results on the datasets compared to the baseline (green) and an oracle (blue). 
The oracles sees the graph from our algorithm and correctly partitions the graph based on the ground truth. 
%TODO{Our methods decreases the split variation of information by a factor of XX\% and only increases the merge variation of information by a factor of XX\% on the test datasets.}
Figure \ref{fig:positive-results} shows some successful merges on the Kasthuri Vol. 2. 
Several of these successful examples combine multiple consecutive segments. 
The third example shows the correction of an oversegmented dendrite. 
Figure \ref{fig:negative-results} shows some errors made. 
In two of these examples the algorithm correctly predicted several merges but made just one error.
In the third example, an error in the initial segmentation propagated in our pipeline. 
In the next three subsections we show how each step in the pipeline contributes to this final result.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct4.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-correct5.png}
	\caption{Some correctly predicted results from our framework.}
	\label{fig:positive-results}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect1.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect2.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect3.png}
	\includegraphics[width=0.85\linewidth]{./figures/multicut-incorrect4.png}
	\caption{Mistakes made by the proposed framework.}
	\label{fig:negative-results}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate1.png}
	\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
	\caption{Example merge candidates.}
	\label{fig:skeleton-results}
\end{figure}

@@

Table \ref{table:classification} shows the precision and recall for all of the datasets. 
Since, our method does not rely on the image data, we can train the network on an anisotropic dataset and get impressive results on an isotropic dataset.

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{Accuracy} \\ \hline
		Kasthuri Training & 0.919 & 0.936 & 0.974 \\
		Kasthuri Testing & 0.737 & 0.717 & 0.907 \\
		FlyEM Vol. 1 & 0.796 & 0.478 & 0.862 \\ 
		FlyEM Vol. 2 & 0.762 & 0.422 & 0.810 \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{table:classification}
\end{table}

@@

Applying a graph-based optimization strategy increases the accuracy over the CNN alone. 
In our test datasets, we note an increase in precision on all datasets. 
For our segmentation problems we prefer a higher precision since it is more difficult to correct merge-errors. 
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all three datasets in relation to the CNN.

\begin{table}[h]
	\centering
	\begin{tabular}{c c c c} \hline
		\textbf{Dataset} & $\Delta$ \textbf{Precision} & $\Delta$ \textbf{Recall} & $\Delta$ \textbf{Accuracy} \\ \hline
		Kasthuri Training & +3.60\% & -0.01\% & +0.60\% \\
		Kasthuri Testing & +7.59\% & -1.77\% & +1.38\% \\
		FlyEM Vol. 1 & +2.68\% & +0.76\% & +0.66\% \\ 
		FlyEM Vol. 2 & +2.22\% & -1.05\% & +0.29\% \\ \hline
	\end{tabular}
	\caption{Precision and recall for the training and three test datasets.}
	\label{table:multicut}
\end{table}
